The Astropy Project

### 2017-12-11 main.tex
clarify why novas is missing. fixes #53

\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
the conversion from FK4 to Galactic coordinates for all pairs of tools.
In this figure, the color of the cell indicates the maximum difference (in
arcseconds) between the two tools over the 1000 longitude-latitude pairs tested.
This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
sub-milliarcsecond differences (light colors, small differences), while PALpy,
pySLALIB, and PyAST also agree amongst themselves.
However, there is an offset of around 0.2\arcsec\space between the two groups.
Finally, PyEphem disagrees with all other packages by 0.4--0.8\arcsec (darker
colors, large differences).
These values are only meant to be illustrative and will change over time as the
benchmarks are refined and the packages updated.

>>>>

\figurename~\ref{fig:coordinate_benchmarks} visualizes the relative accuracy of
the conversion from FK4 to Galactic coordinates for all pairs of tools that
implement this transformation.
In this figure, the color of the cell indicates the maximum difference (in
arcseconds) between the two tools over the 1000 longitude-latitude pairs tested.
This figure shows, for example, that \astropypkg, Kapteyn, and PyTPM agree with
sub-milliarcsecond differences (light colors, small differences), while PALpy,
pySLALIB, and PyAST also agree amongst themselves.
However, there is an offset of around 0.2\arcsec\space between the two groups.
Finally, PyEphem disagrees with all other packages by 0.4--0.8\arcsec (darker
colors, large differences).
These values are only meant to be illustrative and will change over time as the
benchmarks are refined and the packages updated.
